\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-16 article.tex
Fixed wording and grammar

% Make the title bold
\title{\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche}

@@

  In this article we analyze hand techniques in patterns Chon-Ji to Juche
  using tags, and then report our findings of a left arm bias.

@@

  Folder names are in themselves informative, in that, like tags, they
  describe the information held within them\cite{jones:folders}. Furthermore,
  they way folder names relate to each other show a structural relationship
  between directories\cite{mathes:folk}.

@@

  In this section we describe where the data originates. Next we elaborate on
  the approach taken to register and investigate the dataset. Finally, we have
  a look at how each movement has been classified with emphasis on special
  cases.

@@

  We then defined the data models with DataMapper, an Object Relational
  Mapper\footnote{\url{http://www.datamapper.org}} (ORM) written in Ruby. The
  models are Ruby classes with properties and associations. Properties define
  field names and data types in the database, whereas the associations defines
  the relationships and cardinality between the models.

@@

  When it comes to a movement with two separate hand techniques, the
  27\textsuperscript{th} movement of Joong-Gun Tul, being \emph{Nachuo so
  sonbadak noollo makgi}, serves as a nice illustration.

@@

        {\bf Movement 8}, \emph{Gunnun so sang joomuk nopunde sewo jirugi}, is
        tagged as a left and right technique, with $\{left\_technique, \:

@@

        {\bf Movement 20}, \emph{Gunnun sogi}, has only the stance registered

@@

        {\bf Movement 29}, \emph{Kyocha so kyocha joomuk noollo makgi}, is

@@

        {\bf Movement 32}, \emph{Gunnun so sang joomuk dwijibo jirugi}, is
        tagged as a left and right technique, with $\{left\_technique, \:

@@

        {\bf Movement 36}, \emph{Gunnun so sang joomuk dwijibo jirugi}, is
        tagged as a left and right technique, with $\{left\_technique, \:

@@

  Techniques by height follow the same trend when looking at all techniques
  combined or techniques to either side (Figure \ref{fig:height_all}). In
  general, there are more blocks than any other technique. Most of the
  techniques are in the middle section, although there is a greater occurrence
  of strikes in the high section, and very few attacks in the low section.

@@

  Because most techniques are performed in walking, sitting and L stances, the
  graphs in this section have been split into two groups. One group shows the
  majority of techniques (84 \%), while the other visualize techniques in
  every other stance (16 \%).

@@

  There are 14 different motion types registered in our data set. The larger
  part of techniques (76 \%) are performed in normal motion (Figure
  \ref{fig:motion_all}), followed by continuous motion (6 \%) and fast motion
  (4 \%).

@@

% Is it possible to say anything about why there are more techniques with the
% right hand, than with the right?

@@

>>>>

% Make the title bold
\title{\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche}

@@

  In this article we analyze hand techniques in patterns Chon-Ji to Juche
  using tags, and then report our findings of a right arm bias.

@@

  Folder names are in themselves informative, in that, like tags, they
  describe the information held within them\cite{jones:folders}. Furthermore,
  the way folder names relate to each other show a structural relationship
  between directories\cite{mathes:folk}.

@@

  In this section we describe where the data originates. Next we elaborate on
  the approach taken to register and investigate the dataset. Finally, a look
  at how each movement has been classified with emphasis on special cases.

@@

  We then defined the data models with DataMapper, an Object Relational
  Mapper\footnote{\url{http://www.datamapper.org}} (ORM) written in the Ruby
  programming language. The models are Ruby classes with properties and
  associations. Properties define field names and data types in the database,
  whereas the associations defines the relationships and cardinality between
  the models.

@@

  When it comes to a movement with two separate hand techniques, the
  27\textsuperscript{th} movement of Joong-Gun Tul, being \emph{Nachuo so
  sonbadak noollo makgi}, serves as a good illustration.

@@

        {\bf Movement 8}, \emph{Gunnun so sang sewo jirugi}, is tagged as a

@@

        {\bf Movement 20}, \emph{Gunnun so}, has only the stance registered
        although the English description says to ``[e]xtend both hands upward
        as if to grab the opponent's head.''

@@

        {\bf Movement 29}, \emph{Gunnun so kyocha joomuk noollo makgi}, is

@@

        {\bf Movement 32}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as

@@

        {\bf Movement 36}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as

@@

  Techniques by height follow the same trend when looking at all techniques
  combined or techniques to either side. In general, there are more blocks
  than any other technique. Most of the techniques are in the middle section,
  although there is a greater occurrence of strikes in the high section, and
  very few attacks in the low section (Figure \ref{fig:height_all}).

@@

  Because most techniques are performed in walking, sitting and L stances, the
  graphs in this section have been split into two groups. One group shows the
  majority of techniques (84 \%), while the other visualize techniques
  performed in the remaining stances (16 \%).

@@

  There are 14 different motion types registered in our data set. The larger
  part of the techniques (76 \%) are performed in normal motion (Figure
  \ref{fig:motion_all}), followed by continuous motion (6 \%) and fast motion
  (4 \%).

@@

% Is it possible to say anything about why there are more techniques with the
% right hand, than with the left?

@@

% {left_technique, right_technique} should probably have been tagged
% {both_hands} as well.

% Link to the source code.

% Movements with several blocks should have a tag indicating that there are
% more than one block in the movement.
